Review: Adaptive Introgression Expanded the Genetic Base of Crops during post-Domestication Spread

### 2017-07-14 paper.tex
Update paper.tex

What is the genomic architecture of this introgression, and does the architecture suggest that it has been adaptive?
After the hybrization events that lead to introgression, how long might the detectable genomic signals of introgression persist?

At what taxonomic scale does introgression occur?
When do species become so diverged that introgression is either maladaptive or impossible (due to  Dobzhansky-Muller incompatiblities or other mechanisms)?
To what extent does the level of introgression across taxa depend on divergence time and/or mutation load between donor and recipient taxa? \gmj{I think we could include (effective) population size in this list of factors that determine extent of introgression.}

>>>>

What is the genomic architecture of this introgression, and does the architecture suggest that it has been adaptive?
\gmj{Determination of adaptiveness could be accomplished genomically (looking for high LD regions that indicate selective sweeps, or by functional identification.}
%\gmj{Kinds of functional identification?  Knockout experiments, sequence homology with annotated genes, proximity to QTLs?}
After the hybrization events that lead to introgression, how long might the detectable genomic signals of introgression persist?
\gmj{Depends on number of generations, effective population size, mutation rate, recombination rate, patterns and strength of selection.}
\gmj{If an introgression from the progenitor sweeps across the cultivated species, how is it distinguished from a genomic region that is identical by descent and wasn't lost in the domestication process?}

At what taxonomic scale does introgression occur?
When do species become so diverged that introgression is either maladaptive or impossible (due to  Dobzhansky-Muller incompatiblities or other mechanisms)?
To what extent does the level of introgression across taxa depend on divergence time and/or mutation load between donor and recipient taxa? \gmj{I think we could include (effective) population size in this list of factors that determine extent of introgression.}
\gmj{I could also talk about cross-incompatibility factors in maize/teosinte hybridization vs. highly compatible asian rice and its relatives.  I probably wouldn't need a new source for the rice, but I might need to cite a paper about tcb1, ga1, and ga2.}
